---
title: '<span style = ''font-size:14pt;''>**Microbial Communities in the changing vegetation of the Chihuahuan Desert 
**</span>'
subtitle: '<span style = ''font-size:12pt;''> Bacterial Indicator Species
</span>'
author: "Emily Embury"
date: "`r Sys.Date()`"
output: html_document
---
<style type="text/css">
/* Whole document: */ 
body{
  font-size: 12pt;
}
/* Headers */
h1{
  font-size: 15pt;
}
</style>

---

```{r include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,              
  warning = FALSE,       
  message = FALSE,  
  cache = FALSE,        
  fig.align = "center", 
  fig.height = 6,
  fig.width = 9,
  class.source="bg-warning",
  class.output="bg-success"
)

```


# **Import qiime formatted data**
  - https://blog.codyglickman.com/2018/10/qiime2-to-phyloseq.html

```{r import_data}

library(phyloseq)
library(dplyr)
library(tidyverse)
library(vegan)


load("~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/bacteria_dada2_data.RData") 
#contains taxa and otu table


#import metadata
sam <- read.csv("~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/Bacteria/dada2_files/nov_2_metadata.csv", header = TRUE) 
rownames(sam) <- sam$sample.id

#add month_veg row to data
sam$month_veg = paste(sam$month, sam$vegetation, sep="-")

#adjust sample data labels
sam$Vegetation <- factor(sam$vegetation, levels = c("Grass", "Mesquite_grass", "Mesquite"), 
                  labels = c("Grass", "Grass-Mesquite", "Mesquite")) 

sam$Month <- factor(sam$month, levels = c("Oct", "Jan", "Mar", "May", "Jul"), 
                  labels = c("October", "January", "March", "May", "July"))

#compile data into phyloseq object
phylo_raw <- phyloseq(otu_table(seqtab.nochim, taxa_are_rows = FALSE), 
               sample_data(sam), 
               tax_table(taxa))


dna <- Biostrings::DNAStringSet(taxa_names(phylo_raw))
names(dna) <- taxa_names(phylo_raw)
phylo_raw <- merge_phyloseq(phylo_raw, dna)
taxa_names(phylo_raw) <- paste0("ASV", seq(ntaxa(phylo_raw)))
phylo_raw

#Add names to biom table and check phyloseq objects
colnames(tax_table(phylo_raw))= c("Kingdom","Phylum","Class","Order","Family","Genus", "Species")
```
# **remove controls + contaminants**

```{r decontam}
library(decontam)

# threshold 0.5, identifies 6 contaminants
contamdf.prev05 <- isContaminant(phylo_raw, method="prevalence", neg="neg", threshold=0.5)
table(contamdf.prev05$contaminant)

#prune the contaminated taxa
phylo_rm_contaminat <- prune_taxa(!contamdf.prev05$contaminant, phylo_raw)
phylo_rm_contaminat #after

#remove any left over controls 
phylo_rm_contaminat_rm_cntrl = subset_samples(phylo_rm_contaminat, sample.id != "CONTROL1" & sample.id != "CONTROL2" & sample.id != "CONTROL3" & sample.id != 129)


## remove unknowns and archaea, keep only bacteria
bac <- subset_taxa(phylo_rm_contaminat_rm_cntrl, Kingdom == "Bacteria")
phylo_rm_archaea <- prune_taxa(c(taxa_names(bac)), phylo_rm_contaminat_rm_cntrl) 
phylo_rm_archaea 

#get relative abundance
library(microbiome)
phylo_rm_archaea <- phylo_rm_archaea %>% 
          microbiome::transform(transform = "compositional")
```

#**Isolate ASV table from phyloseq**
```{r}
library(tibble)
library(dplyr)
library(phylosmith)

# Morrison 2019 "We also used Indicator Species Analysis (ISA; De Cáceres and Legendre, 2009; De Cáceres et al., 2010) to test for fungal OTUs with ≥25% frequency that had large positive or negative responses to warming in frequency and relative abundance"

# filter taxa to ≥25% frequency
phylo_rm_archaea <- taxa_filter(phylo_rm_archaea, treatment = NULL, subset = NULL,
frequency = 0.25, below = FALSE, drop_samples = TRUE)

# Extract abundance matrix from the phyloseq object
OTU1 = as(otu_table(phylo_rm_archaea), "matrix")
# transpose if necessary
if(taxa_are_rows(phylo_rm_archaea)){OTU1 <- t(OTU1)}
# Coerce to data.frame
OTUdf = as.data.frame(OTU1)



#extract taxa table
taxa = as(tax_table(phylo_rm_archaea), "matrix")
taxadf = as.data.frame(taxa)
taxadf <- tibble::rownames_to_column(taxadf, "sample.id")

# transpose 

#add metadata to OTU table
OTUdf2 <- tibble::rownames_to_column(OTUdf, "sample.id")
OTUdf_merge <- merge(sam, OTUdf2, by.y= "sample.id")


#merge taxa table with otu table
OTU1 = as(otu_table(phylo_rm_archaea), "matrix")
OTU1 = as.data.frame(OTU1)
OTU1 <- tibble::rownames_to_column(OTU1, "sample.id")

OTU_taxa_merge <- merge(OTU1, taxadf, by.y= "sample.id")
```


```{r}
library(indicspecies)
options(max.print=1000000)

# vegetation
sc_g <- indicators(X=OTUdf, cluster=OTUdf_merge$Vegetation, group="Grass", 
                 max.order = 2, 
                 At=0.9, Bt=0.6)
print(sc_g)

#sc2_g <- pruneindicators(sc_g, At=1, Bt=0.8, verbose=TRUE)
#print(sc2_g)


sc_m <- indicators(X=OTUdf, cluster=OTUdf_merge$Vegetation, group="Mesquite", 
                 max.order = 2, 
                 At=0.9, Bt=0.88)
print(sc_m)

sc_mg <- indicators(X=OTUdf, cluster=OTUdf_merge$Vegetation, group="Grass-Mesquite", 
                 max.order = 2, 
                 At=0.8, Bt=0.5)
print(sc_mg)

```

- https://uw.pressbooks.pub/appliedmultivariatestatistics/chapter/isa/
- https://cran.r-project.org/web/packages/indicspecies/vignettes/IndicatorSpeciesAnalysis.html#additional-functions-to-estimate-and-test-the-association-between-species-and-groups-of-sites 




- Morrison 2019 " We also used Indicator Species Analysis (ISA; De Cáceres and Legendre, 2009; De Cáceres et al., 2010) to test for fungal OTUs with ≥25% frequency that had large positive or negative responses to warming in frequency and relative abundance"
