---
title: '<span style = ''font-size:14pt;''>**Microbial Communities in the changing vegetation of the Chihuahuan Desert 
**</span>'
subtitle: '<span style = ''font-size:12pt;''> Bacteria Alpha and Beta Diversity
</span>'
author: "Emily Embury"
date: "`r Sys.Date()`"
output: html_document
---
<style type="text/css">
/* Whole document: */ 
body{
  font-size: 12pt;
}
/* Headers */
h1{
  font-size: 12pt;
}
</style>

---

```{r include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,              
  warning = FALSE,       
  message = FALSE,  
  cache = FALSE,        
  fig.align = "center", 
  fig.height = 4,
  fig.width = 6,
  class.source="bg-warning",
  class.output="bg-success"
)

```


# **Import qiime formatted data**
  - https://blog.codyglickman.com/2018/10/qiime2-to-phyloseq.html

```{r}
library(phyloseq)

biom_data_raw <- import_biom(BIOMfilename = "Bacteria/bacteria_taxa_table_raw.biom", refseqfilename = "Bacteria/bacteria-dna-sequences-rare.fasta")

mapping_file <- import_qiime_sample_data(mapfilename = "Bacteria/CORRECTED_metadata.tsv")



# Merge the OTU and mapping data into a phyloseq object
phylo_raw <- merge_phyloseq(biom_data_raw, mapping_file)
#Add names to biom table and check phyloseq objects
colnames(tax_table(phylo_raw))= c("Kingdom","Phylum","Class","Order","Family","Genus", "Species")
rank_names(phylo_raw)

depths <- sample_sums(phylo_raw)
```
# **remove controls + contaminants**

```{r}
library(decontam)

# threshold 0.5, identifies 9 contaminants
contamdf.prev05 <- isContaminant(phylo_raw, method="prevalence", neg="neg", threshold=0.5)
table(contamdf.prev05$contaminant)

#prune the contaminated taxa
phylo_rm_contaminat <- prune_taxa(!contamdf.prev05$contaminant, phylo_raw)
phylo_rm_contaminat #after

#remove any left over controls so they dont impact normalization
phylo_rm_contaminat_rm_cntrl = subset_samples(phylo_rm_contaminat, sample.id != "CONTROL1-S1" & sample.id != "CONTROL2-S79" & sample.id != "CONTROL3-S109")

```


# **Alpha Diversity**
  - https://joey711.github.io/phyloseq/plot_richness-examples.html
  - https://rpubs.com/lconteville/713954 


- https://doi.org/10.1016/j.resmic.2018.03.004 states that shannon is the best index to use

- "Simpson’s index (D) Estimator of species richness and species evenness: more weight on species evenness" -- https://doi.org/10.4014/jmb.1709.09027 

```{r}

richness <- estimate_richness(phylo_rare)
alpha_veg <- plot_richness(phylo_rare, x = "vegetation", measures = c("Simpson"))
alpha_veg

#Shannon
anova.sh.veg = aov(richness$Shannon ~ sample_data(phylo_rare)$vegetation)
summary(anova.sh.veg)

TukeyHSD(anova.sh.veg)

#Simpson
anova.smp.veg = aov(richness$Simpson ~ sample_data(phylo_rare)$vegetation)
summary(anova.smp.veg)

TukeyHSD(anova.smp.veg)


#Chao1
anova.ch.veg = aov(richness$Chao1 ~ sample_data(phylo_rare)$vegetation)
summary(anova.ch.veg)

TukeyHSD(anova.ch.veg)

```


# **Beta Diversity**

#http://evomics.org/wp-content/uploads/2016/01/phyloseq-Lab-01-Answers.html

- adonis = essentially an ANOVA for distances
- betadisper is a test of normality
    - so non-significant is good because it data assumptions, therefore the adois can be trusted more
    - see https://deneflab.github.io/MicrobeMiseq/demos/mothur_2_phyloseq.html#permanova for more

- "Furthermore, beta-diversity measures might be chosen to make it easier to assess a specific hypothesis, such as changes in microbiome composition over time. For example, a Bray Curtis distance that uses all the abundance differences may be more sensitive to examine gradients of diversity with location or time" -- https://doi.org/10.1016/j.csbj.2022.04.032 

-  https://doi.org/10.1111/2041-210X.13115 = proportions are the best way to normalize for BC distance in community analyses
```{r}

library(vegan)
library(phyloseq)
library(tidyverse)
library(agricolae)
library(rcompanion)
library(microbiomeMarker)

# normalize data with proportions (aka Total Sum Normalization)

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("microbiomeMarker")

# calculate Bray-Curtis distance using the vegan package
DistBC <- distance(phylo_rm_contaminat_rm_cntrl, method = "bray")

#ordinate bray distances
ordBC <- ordinate(phylo_rm_contaminat_rm_cntrl, method = "NMDS", distance = DistBC)

#plot distances
plot_ordination(phylo_rm_contaminat_rm_cntrl, ordBC, color = "vegetation") + 
  geom_point() +
  ggtitle("NMDS: Bray-Curtis")+
    stat_ellipse(size =.5) 



#stats

#create data frame of metadata
sampleDF <-  data.frame(sample_data(phylo_rm_contaminat_rm_cntrl))

# adonis : Analysis of variance using distance matrices
adonis2(DistBC ~ sampleDF$vegetation, data = sampleDF)

library(pairwiseAdonis)
pairwise.adonis(DistBC, phyloseq::sample_data(phylo_rm_contaminat_rm_cntrl)$vegetation)

# betadisper - analysis of multivariate homogeneity of group dispersion (variances)
beta <- betadisper(DistBC, sampleDF$vegetation)
permutest(beta)


```