---
title: '<span style = ''font-size:14pt;''>**Microbial Communities in the changing vegetation of the Chihuahuan Desert 
**</span>'
subtitle: '<span style = ''font-size:12pt;''>Exploratory Data Analyses
</span>'
author: "Emily Embury"
date: "`r Sys.Date()`"
output: pdf_document
---
<style type="text/css">
/* Whole document: */ 
body{
  font-size: 12pt;
}
/* Headers */
h1{
  font-size: 12pt;
}
</style>

---

```{r include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,              
  warning = FALSE,       
  message = FALSE,  
  cache = FALSE,        
  fig.align = "center", 
  fig.height = 4,
  fig.width = 5,
  class.source="bg-warning",
  class.output="bg-success"
)

```

# **Soil Temperature**

- Soil temperature measurements

- Soil temperature was measured using a temperature probe at a depth of 3.75in.

- A, B, C correspond with replicates within plots


```{r}
soil_temp <- read.csv("Raw_data/soil_temp/Soil_temperature.csv")

#add column to average temp in each plot
library(dplyr)
soil_temp_avg <- mutate(soil_temp, mean_col = rowMeans(select(soil_temp,
                                              c(Celsius_A,Celsius_B,Celsius_C)),
                                              na.rm = TRUE))

#plot monthly averages
library(ggplot2)

ggplot(soil_temp_avg, aes(x=factor(Vegetation, 
                                   level=c('Grass', 
                                           'Mesquite_Grass', 
                                           'Mesquite')), #change order of x-axis
                          y=mean_col))+
  geom_bar(position="dodge", stat="identity")+
  facet_wrap(~factor(Month, levels = c("October", "January", "March", 
                                       "May", "July")))+
  xlab("Vegetation") + # change x axis label
  ylab("Temperature (C)") # change y axis label

```


# **Soil pH**

- There were issues with the pH soil probe so all data using that probe will not be included in any analyses

- All pH measurements are from soil samples sent to RegenAg


```{r}
soil_ph <- read.csv("Raw_data/soil_chem/ph_for_r.csv", header = TRUE)

#plot data
library(ggplot2)

ggplot(soil_ph, aes(x=factor(Vegetation, 
                                   level=c('Grass', 
                                           'Mesquite-Grass', 
                                           'Mesquite')), #change order of x-axis
                          y=pH))+
  geom_boxplot()+
  facet_wrap(~factor(Month, levels = c("October", "January", "March", 
                                       "May", "July")))+
  stat_summary(fun.y=mean, geom="point", shape=23, color="red", fill="yellow") +
  xlab("Vegetation") + # change x axis label
  ylab("pH") # change y axis label

```



# **C:N Levels**

- All C:N measurements are from soil samples sent to RegenAg


```{r}
soil_CN <- read.csv("Raw_data/soil_chem/C_N_for_r.csv", header = TRUE)

#add column of C:N ratio
soil_CN <- transform(soil_CN, C_N = soil_CN$C / soil_CN$N)

#plot C:N ratio
library(ggplot2)

ggplot(soil_CN, aes(x=factor(Vegetation, 
                                   level=c('Grass', 
                                           'Mesquite-Grass', 
                                           'Mesquite')), #change order of x-axis
                          y=C_N))+
  geom_boxplot()+
  facet_wrap(~factor(Month, levels = c("October", "January", "March", 
                                       "May", "July")))+
  stat_summary(fun.y=mean, geom="point", shape=23, color="red", fill="yellow") +
  xlab("Vegetation") + # change x axis label
  ylab("C:N") # change y axis label
```

# **SECTION TITLE HERE**

ENTER TEXT HERE


```{r}
#ENTER CODE HERE
```