---
title: '<span style = ''font-size:14pt;''>**Microbial Communities in the changing vegetation of the Chihuahuan Desert 
**</span>'
subtitle: '<span style = ''font-size:12pt;''>Exploratory Data Analyses
</span>'
author: "Emily Embury"
date: "`r Sys.Date()`"
output: pdf_document
---
<style type="text/css">
/* Whole document: */ 
body{
  font-size: 12pt;
}
/* Headers */
h1{
  font-size: 12pt;
}
</style>

---

```{r include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,              
  warning = FALSE,       
  message = FALSE,  
  cache = FALSE,        
  fig.align = "center", 
  fig.height = 8,
  fig.width = 8,
  class.source="bg-warning",
  class.output="bg-success"
)

```

# **Soil Temperature**

- Soil temperature measurements

- Soil temperature was measured using a temperature probe at a depth of 3.75in.

- A, B, C correspond with replicates within plots


```{r}
soil_temp <- read.csv("Raw_data/soil_temp/Soil_temperature_2.csv")

#get standard deviation for error bars
library(Rmisc)
soil_temp_sum <- summarySE(soil_temp, measurevar = "Celsius", groupvars=c("Month","Vegetation"))

#plot monthly averages
library(ggplot2)

ggplot(soil_temp_sum, aes(x=factor(Vegetation, 
                                   level=c('Grass', 
                                           'Mesquite_Grass', 
                                           'Mesquite')), #change order of x-axis
                          y=Celsius))+
  geom_bar(position="dodge", stat="identity")+
  facet_wrap(~factor(Month, levels = c("October", "January", "March", 
                                       "May", "July")))+
  xlab("Vegetation") + # change x axis label
  ylab("Temperature (C)") +# change y axis label
  geom_errorbar(aes(ymin=Celsius-se, ymax=Celsius+se), width=.1) 

#add error bars


```


# **Soil pH**

- There were issues with the pH soil probe so all data using that probe will not be included in any analyses

- All pH measurements are from soil samples sent to RegenAg


```{r}
soil_ph <- read.csv("Raw_data/soil_chem/ph_for_r.csv", header = TRUE)

#plot data
library(ggplot2)

pH_plot <- ggplot(soil_ph, aes(x=factor(Vegetation, 
                                   level=c('Grass', 
                                           'Mesquite-Grass', 
                                           'Mesquite')), #change order of x-axis
                          y=pH))+
  geom_boxplot()+
  facet_wrap(~factor(Month, levels = c("October", "January", "March", 
                                       "May", "July")))+
  stat_summary(fun.y=mean, geom="point", shape=23, color="red", fill="yellow") +
  xlab("Vegetation") + # change x axis label
  ylab("pH") # change y axis label

#add P values
library(ggpubr)
library(tidyverse)

mycomparisons_veg <- list(c("Grass", "Mesquite-Grass"),
                          c("Mesquite",  "Mesquite-Grass"), 
                          c("Grass", "Mesquite")) #groupings for ANOVA

pH_plot + stat_compare_means(comparisons = mycomparisons_veg, size = 3, label.y = 5, step.increase = .3)+
  stat_compare_means(method = "anova", label.y = 1, size = 3) # add anova values to plot
```

# **Electrical conductivity**

```{r}
e_conduct <- read.csv("Raw_data/soil_chem/Electrical_conductivity_for_r.csv", header = TRUE)

#plot data
library(ggplot2)

e_conduct_plot <- ggplot(e_conduct, aes(x=factor(Vegetation, 
                                   level=c('Grass', 
                                           'Mesquite-Grass', 
                                           'Mesquite')), #change order of x-axis
                          y=Electrical.Conductivity))+
  geom_boxplot()+
  facet_wrap(~factor(Month, levels = c("October", "January", "March", 
                                       "May", "July")))+
  stat_summary(fun.y=mean, geom="point", shape=23, color="red", fill="yellow") +
  xlab("Vegetation") + # change x axis label
  ylab("Electrical Conductivity mmho/cm") # change y axis label

#add P values
library(ggpubr)
library(tidyverse)

mycomparisons_veg <- list(c("Grass", "Mesquite-Grass"),
                          c("Mesquite",  "Mesquite-Grass"), 
                          c("Grass", "Mesquite")) #groupings for ANOVA

e_conduct_plot + stat_compare_means(comparisons = mycomparisons_veg, label.y = 0.21, step.increase = .1, size = 3)+
  stat_compare_means(method = "anova", label.y = .05) # add anova values to plot
```

# **C:N Levels**

- All C:N measurements are from soil samples sent to RegenAg


```{r}
soil_CN <- read.csv("Raw_data/soil_chem/C_N_for_r.csv", header = TRUE)

#add column of C:N ratio
soil_CN <- transform(soil_CN, C_N = soil_CN$C / soil_CN$N)

#plot C:N ratio
library(ggplot2)

CN_plot <- ggplot(soil_CN, aes(x=factor(Vegetation, 
                                   level=c('Grass', 
                                           'Mesquite-Grass', 
                                           'Mesquite')), #change order of x-axis
                          y=C_N))+
  geom_boxplot()+
  facet_wrap(~factor(Month, levels = c("October", "January", "March", 
                                       "May", "July")))+
  stat_summary(fun.y=mean, geom="point", shape=23, color="red", fill="yellow") +
  xlab("Vegetation") + # change x axis label
  ylab("C:N")+ # change y axis label
  ylim(0, 17) #change y-axis scale so p values can fit in plot


#add P values
library(ggpubr)
library(tidyverse)

mycomparisons_veg <- list(c("Grass", "Mesquite-Grass"),
                          c("Mesquite",  "Mesquite-Grass"), 
                          c("Grass", "Mesquite")) #groupings for ANOVA

CN_plot + stat_compare_means(comparisons = mycomparisons_veg, size = 3, step.increase = .19)+
  stat_compare_means(method = "anova", label.y = 1, size = 3) # add anova values to plot
```

# **PLFA**
    - Phospholipid Fatty Acid Analysis

    - Thoughts so far (as of 10/5/2023): Vegetation does not seem to be a significant driver of biomass variation. Instead, seasonality appears to be a stronger driver of biomass variation.

- Fungal and Bacterial Biomass Percentage
```{r}
PLFA_fun_bac <- read.csv("Raw_data/PLFA/All_PLFA_fun_back.csv")

library(ggplot2)

PLFA_plot <- ggplot(PLFA_fun_bac,
            aes(x=factor(Month, levels = c("October", "January", "March", "May", "July")), y = Total_Percent_Biomass,
                fill = factor(Month, levels = c("October", "January", "March", "May", "July"))))+  #change bar order
  geom_boxplot(show.legend = FALSE)+
  facet_grid(factor(Vegetation, levels=c('Grass', 'Mesquite-Grass', 'Mesquite'))~ Type)+
  scale_y_continuous(labels = scales::percent_format(scale = 1))+ # change y-axis to percentage
  theme(axis.title.x = element_blank(), axis.text.x = element_text(), axis.ticks.x   = element_blank()) + #remove x-axis title
  ylab("% of Total Biomass")+ # change y axis label
  ggtitle ("% of Fungi and Bacteria in Total Biomass Across Vegetation Types and Sampleing Periods") + #change title
  #theme( text = element_text(size = 20)) + # change sizes for poster presentation
  scale_fill_manual(values=c("October" ="#c1292e", "January" = "#e1bc29", "March" = "#679436", "May" = "#4895ef" , "July" ="#8187dc"), name = "Month") #add custom colors and change legend name

PLFA_plot



mod.plfa <- aov(PLFA_fun_bac$Total_Percent_Biomass ~ PLFA_fun_bac$Type*PLFA_fun_bac$Month*PLFA_fun_bac$Vegetation)
summary(mod.plfa)

tuk.plfa <- TukeyHSD(mod.plfa)

library(dplyr)
### filter TukeyHSD results to only show significant values
x <- as.data.frame(tuk.plfa$`PLFA_fun_bac$Type:PLFA_fun_bac$Month:PLFA_fun_bac$Vegetation`) %>%
  filter(`p adj` < .05)

```

- Total Biomass in ng/g

  - remove outlier:
  Mesquite	January	M2_a_Jan	28018.25
```{r}

PLFA_total <- read.csv("Raw_data/PLFA/Total_biomass.csv")

PLFA_plot_total <- ggplot(PLFA_total,aes(x=Month, y = Total_Biomass,
  fill = factor(Month, levels = c("October", "January", "March", "May", "July")))) + 
  geom_boxplot()+
  facet_wrap(~factor(Vegetation, levels=c('Grass', 'Mesquite-Grass', 'Mesquite')))+
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank())+
  ylab("Total Biomass (ng/g)")+ # change y axis label
  ggtitle ("Total Microbial Biomass Across Vegetation Types and Sampleing Periods") + #change title
  scale_fill_manual(values=c("October" ="#c1292e", "January" = "#e1bc29", "March" = "#679436", "May" = "#4895ef" , "July" ="#8187dc"), name = "Month") #add custom colors and change legend name


PLFA_plot_total

mod.plfa.tot <- aov(PLFA_total$Total_Biomass ~ PLFA_total$Vegetation*PLFA_total$Month)
summary(mod.plfa.tot)

tot.tuk <- TukeyHSD(mod.plfa.tot)

library(dplyr)
library(tidyverse)


### filter TukeyHSD results to only show significant values
as.data.frame(tot.tuk$`PLFA_total$Vegetation:PLFA_total$Month`) %>%
  filter(`p adj` < .05)

as.data.frame(tot.tuk$`PLFA_total$Vegetation`) %>%
  filter(`p adj` < .05)

as.data.frame(tot.tuk$`PLFA_total$Month`) %>%
  filter(`p adj` < .05)

```

# **Respiration**

" Also not super important for this report. But for your thesis, write microbial respiration in the y axis and then add in parenthesis (CO2 g-1 h-1)" -- from Adriana


- Respiration measured from litter bags
- Litter bags placed into Mason jar respiration chambers and incubated for 45 minutes
- Calculations:
  - How to transform CO2 data in ppm to rate of CO2 g-1 of biomass h-1
    - You have:
      - CO2start (ppm = umol/mol)
      - CO2end (umol/mol)
      - Interval (hr)
      - Volume of air in jar = Total volume of jar minus volume of biomass (ml) (for example if we have a jar of 25 mls and we have 5 mls of media, then the volume of the air would be 20 mls).
      - Density of CO2 at STP = 44.0 gr/22400 ml

  - CO2 flux = (CO2end-CO2start) / interval * Volume * Density
  - The units will be CO2grams hr-1. You can then divide by the biomass to your desired result.


```{r}
respiration <- read.csv("Raw_data/respiration/CO2_adjusted_w_start.csv")


# CO2_measure_for_R is values without adjusting for start CO2
# CO2_raw.csv is values in jar without adjusting for biomass and not including start C02
# CO2_adjust_w_start is values adjusted for biomass and start CO2
# CO2_site is values of empty jar

respiration_plot <- ggplot(respiration, aes(x=factor(Vegetation, 
                                   level=c('Grass', 
                                           'Mesquite Grass', 
                                           'Mesquite')), y=Respiration, fill = Vegetation))  + #plot CO2 by vegetation type
  geom_boxplot(lwd=.8)  + # add box plot
  theme_bw()+ # remove grey background
  facet_wrap(~Month)+ #group by month
  ylab("CO2 g-1 of biomass h-1")+ # change y axis label
  xlab("Vegetation")+
  ggtitle ("CO2 Measurements Across Seasons and Vegetation")+ #change title
  scale_fill_manual(values=c("Mesquite" ="#c04d27", "Grass" = "#edba1d", "Mesquite Grass" = "#47c0c4"))#add custom colors 

  

mycomparisons <- list( c("Grass", "Mesquite Grass"),  c("Mesquite", "Mesquite Grass"), c("Grass", "Mesquite")) #groupings for ANOVA

respiration_plot + stat_compare_means(comparisons = mycomparisons, size =3)

```


# **Litter Decomposition**

"Not too important for this report, but for your thesis, write days instead of collection period in the x axis." -- from Adriana

Mass loss from litter bags


Collection Periods:

  - a = 87 days of decomposition
  - b = 145 days of decomposition
  - c = 207 days of decomposition
  - d = 269 days of decomposition

```{r}
litter_seived <- read.csv("Raw_data/litter/Litter_bags_seived_rm_open.csv")
litter <- read.csv("Raw_data/litter/Litter_bags_rm_open.csv")
litter_rm_mesh1 <- read.csv("Raw_data/litter/Litter_bags_seived_rm_open_rm_mesh1.csv")

library(ggplot2)

#get standard deviation for error bars
library(Rmisc)
litter_sum_seived <- summarySE(litter_seived, measurevar = "Biomass_change", groupvars=c("Collection_period","Vegetation"))


litter_plot_seived <- ggplot(litter_sum_seived, aes(x= Collection_period, y = Biomass_change, group = Vegetation))+
  geom_line(aes(color=Vegetation))+
  geom_point()+
  xlab("Collection Period") + # change x axis label
  ylab("Average Change in Biomass (g)")+ # change y axis label
  ggtitle("Leaf Litter Mass Lost Following Microbial Decomposition in
          Different Vegetation Types")+
  scale_color_manual(values=c("Mesquite" ="#c04d27", "Grass" = "#edba1d", "Mesquite-Grass" = "#47c0c4"))+
    theme( text = element_text(size = 20)) +
  geom_errorbar(aes(ymin=Biomass_change-se, ymax=Biomass_change+se, color = Vegetation), width=.1) 
  
##############
litter_sum <- summarySE(litter, measurevar = "Biomass_change", groupvars=c("Collection_period","Vegetation"))


litter_plot <- ggplot(litter_sum, aes(x= Collection_period, y = Biomass_change, group = Vegetation))+
  geom_line(aes(color=Vegetation))+
  geom_point()+
  xlab("Collection Period") + # change x axis label
  ylab("Average Change in Biomass (g)")+ # change y axis label
  ggtitle("litter mass not seived")+
  scale_color_manual(values=c("Mesquite" ="#c04d27", "Grass" = "#edba1d", "Mesquite-Grass" = "#47c0c4"))+ #add custom colors
  geom_errorbar(aes(ymin=Biomass_change-se, ymax=Biomass_change+se, color = Vegetation), width=.1) 

##############
litter_sum_rm_mesh1 <- summarySE(litter_rm_mesh1, measurevar = "Biomass_change", groupvars=c("Collection_period","Vegetation"))


litter_plot_rm_mesh1 <- ggplot(litter_sum_rm_mesh1, aes(x= Collection_period, y = Biomass_change, group = Vegetation))+
  geom_line(aes(color=Vegetation))+
  geom_point()+
  xlab("Collection Period") + # change x axis label
  ylab("Average Change in Biomass (g)")+ # change y axis label
  ggtitle("litter mass seived + mesh 1 removed")+
  scale_color_manual(values=c("Mesquite" ="#c04d27", "Grass" = "#edba1d", "Mesquite-Grass" = "#47c0c4"))+ #add custom colors
  geom_errorbar(aes(ymin=Biomass_change-se, ymax=Biomass_change+se, color = Vegetation), width=.1) 
  
  
litter_plot
litter_plot_seived
litter_plot_rm_mesh1 
```

# **Temperature, humidity, and precipitation data** 

From John Anderson:

- Study 611 Plot G3 -> Study 548 CSIS Block-8 
  - Distance from plot to met station:  ~92m NNW
- Study 611 Plot MG3 -> Study 548 CSIS Block-7   
  - Distance from plot to met station:  ~192m SW
- Study 611 Plot M1 -> Study 548 CSIS Block-11    
  - Distance from plot to met station:  ~135m NNW

**Block 8** Grass site

Anderson, J. 2023. Jornada Basin LTER Cross-scale Interactions Study (CSIS) Block 8 meteorological station: Daily summary data: 2013 - ongoing ver 33. Environmental Data Initiative. https://doi.org/10.6073/pasta/bf8b5899b2e6bace4ceefa48fd3c970b (Accessed 2023-09-10).

**Block 7** Mesquite-Grass

Anderson, J. 2023. Jornada Basin LTER Cross-scale Interactions Study (CSIS) Block 7 meteorological station: Daily summary data: 2013 - ongoing ver 35. Environmental Data Initiative. https://doi.org/10.6073/pasta/c6d90223879a86a0825e3aeddb4b1619 (Accessed 2023-09-11).

**Block 11** Mesquite

Anderson, J. 2023. Jornada Basin LTER Cross-scale Interactions Study (CSIS) Block 11 meteorological station: Daily summary data: 2013 - ongoing ver 32. Environmental Data Initiative. https://doi.org/10.6073/pasta/c11ab044ada8ea13b5e6d1d2e20e7494 (Accessed 2023-09-11).

```{r}
library(ggplot2)
### Block 7 - Mesquite-grass

weather <- read.csv("Raw_data/JRN_temp_humid/all_weather.csv", header = TRUE)
weather$Date <- as.Date(weather$Date)

library(lubridate)
### daily average temperature
ggplot(weather, aes(x=Date, y=Air_TempC_Avg, color = Month))+
  geom_point() +
  scale_x_date(date_labels = "%B", date_breaks = "1 month")+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  ggtitle("2022-2023 Monthly Temperature")+
  ylab("Average Air Temperature (C)")+
  xlab("Month")+
  scale_colour_manual(values=c("October" ="#c1292e", "January" = "#e1bc29", "March" = "#679436", "May" = "#4895ef" , "July" ="#8187dc"))


### daily average humidity
ggplot(weather, aes(x=Date, y=Relative_Humidity_Avg, color = Month))+
  geom_point() +
  scale_x_date(date_labels = "%B", date_breaks = "1 month")+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  ggtitle("2022-2023 Monthly Relative Humidity")+
  ylab("Average Relative Humidity")+
  xlab("Month")+
  scale_colour_manual(values=c("October" ="#c1292e", "January" = "#e1bc29", "March" = "#679436", "May" = "#4895ef" , "July" ="#8187dc"))


### daily total precipitation
ggplot(weather[which(weather$Ppt_mm_Tot >0),], aes(x=Date, y=Ppt_mm_Tot, color = Month))+
  geom_point() +
  scale_x_date(date_labels = "%B", date_breaks = "1 month")+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  ggtitle("2022-2023 Precipitation")+
  ylab("Precipitation (mm)")+
  xlab("Month")+
  scale_colour_manual(values=c("October" ="#c1292e", "January" = "#e1bc29", "March" = "#679436", "May" = "#4895ef" , "July" ="#8187dc"))




#get average temperature for three site types to test for significant differences
library(plyr)
temp_by_siteID<-ddply(weather,c("Month","SiteID"),summarise,mean=mean(Air_TempC_Avg))

aov_temp <- aov(temp_by_siteID$mean ~ temp_by_siteID$Month*temp_by_siteID$SiteID)
summary(aov_temp)

    # no siginificant variation between site ID


#get average humidity for three site types to test for significant differences
library(plyr)
rh_by_siteID<-ddply(weather,c("Month","SiteID"),summarise,mean=mean(Relative_Humidity_Avg))

aov_rh <- aov(rh_by_siteID$mean ~ rh_by_siteID$SiteID*rh_by_siteID$Month)
summary(aov_rh)

```

# **Soil Water Content**

**Block 8** Grass site
Duniway, M. 2023. Jornada Basin LTER Cross-scale Interactions Study (CSIS) Block 8 meteorological station: Daily average soil volumetric water content data: 2013 - ongoing ver 33. Environmental Data Initiative. https://doi.org/10.6073/pasta/e6c6ad8289d5da3019c6a8b5d3a9a42d (Accessed 2023-09-11).


**Block 7** Grass-mesquite site

Duniway, M. 2023. Jornada Basin LTER Cross-scale Interactions Study (CSIS) Block 7 meteorological station: Daily average soil volumetric water content data: 2013 - ongoing ver 34. Environmental Data Initiative. https://doi.org/10.6073/pasta/8ef8d92977a00665af194d09eaedc789 (Accessed 2023-09-11).


**Block 11** Mesquite site

Duniway, M. 2023. Jornada Basin LTER Cross-scale Interactions Study (CSIS) Block 11 meteorological station: Daily average soil volumetric water content data: 2013 - ongoing ver 35. Environmental Data Initiative. https://doi.org/10.6073/pasta/501c5045cfb19930f9812b941cc98478 (Accessed 2023-09-11).




# **Vegetation Cover** 

- vegetation cover calculated from drone images
- data for each month is the percentage vegetation cover of all three plots
- sum vegetation/sum of plot area *100

```{r}
vegetation <- read.csv("Raw_data/vegetation_cover/all_months.csv", head = TRUE)

#calculate average of all months for each vegetation type
library(dplyr)
vegetation$Means <-apply(vegetation [,3:7], 1 ,mean)

vegetation$SiteID <- factor(vegetation$SiteID, levels = c("Grass", "Mesquite_Grass", "Mesquite"), 
                  labels = c("Grass", "Mesquite Grass", "Mesquite"))

#build pie chart
library(ggplot2)
library(ggeasy)
library(ggrepel)
library(tidyverse)

m_label <- c("Mesquite Grass")
names(m_label) <- c("Mesquite_Grass")

ggplot(vegetation, aes(x="", y=Means, fill=Vegetation)) +
  geom_bar(stat="identity", width=1) +
  facet_wrap(~factor(SiteID, levels = c("Grass", "Mesquite Grass", "Mesquite")), strip.position = "bottom")+
  coord_polar("y", start=0) +
  ggtitle("% Vegetation Cover in Study Sites")+
  theme_minimal()+
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank(),
        strip.text.x = element_text(size = 10))+
  geom_col(width = 1, color = 1) +
  geom_text(aes(x = 1.15, label = paste0(round(Means, digits = 1), "%")), size=3.2,fontface='bold', 
            position = position_stack(vjust = 0.5))+
  ggeasy::easy_center_title()+
  scale_fill_manual(values=c("Mesquite" ="#c1292e", "Bare" = "#e1bc29", "Grass" = "#679436"), name = "Vegetation") #add custom colors


```
