---
title: '<span style = ''font-size:14pt;''>**Microbial Communities in the changing vegetation of the Chihuahuan Desert 
**</span>'
subtitle: '<span style = ''font-size:12pt;''> Fungal Co-occurance Network
</span>'
author: "Emily Embury"
date: "`r Sys.Date()`"
output: html_document
---
<style type="text/css">
/* Whole document: */ 
body{
  font-size: 12pt;
}
/* Headers */
h1{
  font-size: 15pt;
}
</style>

---

```{r include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,              
  warning = FALSE,       
  message = FALSE,  
  cache = FALSE,        
  fig.align = "center", 
  fig.height = 6,
  fig.width = 9,
  class.source="bg-warning",
  class.output="bg-success"
)

```

# **Import formatted data**

```{r import_data}

library(phyloseq)
library(dplyr)
library(tidyverse)
library(vegan)


load("~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/fungi_dada2_data.RData") 
#contains taxa and otu table


#import metadata
sam <- read.csv("~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/Fungi/fungi_oct_28_metadata.csv", header = TRUE) 
rownames(sam) <- sam$sample.id

#add month_veg row to data
sam$month_veg = paste(sam$month, sam$vegetation, sep="-")

#adjust sample data labels
sam$Vegetation <- factor(sam$vegetation, levels = c("Grass", "Mesquite_grass", "Mesquite"), 
                  labels = c("Grass", "Grass-Mesquite", "Mesquite")) 

sam$Month <- factor(sam$month, levels = c("Oct", "Jan", "Mar", "May", "Jul"), 
                  labels = c("October", "January", "March", "May", "July"))

#compile data into phyloseq object
phylo_raw <- phyloseq(otu_table(seqtab.nochim, taxa_are_rows = FALSE), 
               sample_data(sam), 
               tax_table(taxa))


dna <- Biostrings::DNAStringSet(taxa_names(phylo_raw))
names(dna) <- taxa_names(phylo_raw)
phylo_raw <- merge_phyloseq(phylo_raw, dna)
taxa_names(phylo_raw) <- paste0("ASV", seq(ntaxa(phylo_raw)))
phylo_raw

#Add names to biom table and check phyloseq objects
colnames(tax_table(phylo_raw))= c("Kingdom","Phylum","Class","Order","Family","Genus", "Species")
```

# **remove controls + contaminants**

```{r decontam}
library(decontam)

# threshold 0.5, identifies 0 contaminants
contamdf.prev05 <- isContaminant(phylo_raw, method="prevalence", neg="neg", threshold=0.5)
table(contamdf.prev05$contaminant)


#remove any left over controls so they don't impact rarefy
#remove sample 129 and 93 as it had very low reads after filtering, don't want them to impact rarefy
phylo_rm_cntrl = subset_samples(phylo_raw, sample.id != "Control1" & sample.id != "ControlL2")

```

# **build network from phyloseq object**
- https://github.com/zdk123/SpiecEasi
- https://psbweb05.psb.ugent.be/conet/microbialnetworks/spieceasi.php

- https://rdrr.io/github/taowenmicro/ggClusterNet/man/corMicro.html (ggClusterNet)


**this** paper has code availability https://doi.org/10.1038/s41522-021-00263-y
          https://github.com/bing-g/AD-BW-network/blob/main/code-co-occurrence-network.R 
          

***this** paper also has code availability https://doi.org/10.1002/imt2.71 (much better detail will follow this)




#**Generate Network**

https://chiliubio.oschina.io/microeco_tutorial/model-based-class.html#other-functions : 
SPIEC-EASI (SParse InversE Covariance Estimation for Ecological Association Inference) approach of SpiecEasi R package (Kurtz et al. 2015) has two network construction approaches based on graph model, which relies on algorithms for sparse neighborhood and inverse covariance selection. See https://github.com/zdk123/SpiecEasi for the package installation. It is very slow for SpiecEasi_method = ‘glasso’ when there is a large number (such as hundreds to thousands) according to our test experience.


SpiecEasi: https://github.com/zdk123/SpiecEasi

#protocol forSpiecEasi  https://experiments.springernature.com/articles/10.1007/978-1-0716-1040-4_14


- *"The function cal_sum_links can sum the links (edge) number from one taxa to another or within the same taxa. The function plot_sum_links is used to show the result from the function cal_sum_links. This is very useful to fast see how many nodes are connected between different taxa or within one taxa. In terms of ‘Phylum’ level in the tutorial, the function cal_sum_links() sum the linkages number from one Phylum to another Phylum or the linkages in the same Phylum. So the numbers along the outside of the circular plot represent how many edges or linkages are related with the Phylum. For example, in terms of Proteobacteria, there are roughly total 900 edges associated with the OTUs in Proteobacteria, in which roughly 200 edges connect both OTUs in Proteobacteria and roughly 150 edges connect the OTUs from Proteobacteria with the OTUs from Chloroflexi."* -- https://chiliubio.github.io/microeco_tutorial/model-based-class.html 

```{r}
library(SpiecEasi)
library(file2meco)
library(mia)
library(dplyr)
library(microeco)
library(magrittr)
library(meconetcomp)


## cross-network analysis
rel_meco <- file2meco::phyloseq2meco(phylo_rm_cntrl)

all <- trans_network$new(dataset = rel_meco, cor_method = NULL, taxa_level = "OTU", filter_thres = 0.0001)

#######
#tutorial: https://chiliubio.oschina.io/microeco_tutorial/meconetcomp-package.html
soil_amp_network <- list()

# select samples of "Grass" group
# use clone to get a deep copy of rel_meco (R6 object)
tmp <- clone(rel_meco)
# change sample_table directly
tmp$sample_table %<>% subset(Vegetation == "Grass")
# trim all files in the object
tmp$tidy_dataset()
# use filter_thres parameter to filter the feature with low relative abundance
tmp <- trans_network$new(dataset = tmp, cor_method = "spearman", filter_thres = 0.0007)
# COR_p_thres represents the p value threshold
# COR_cut denotes the correlation coefficient threshold
tmp$cal_network(network_method = "SpiecEasi")
# put the network into the list
soil_amp_network$Grass <- tmp

# select samples of "Mesquite" group
tmp <- clone(rel_meco)
tmp$sample_table %<>% subset(Vegetation == "Mesquite")
tmp$tidy_dataset()
tmp <- trans_network$new(dataset = tmp, cor_method = "spearman", filter_thres = 0.0007)
tmp$cal_network(network_method = "SpiecEasi")
soil_amp_network$Mesquite <- tmp


# select samples of "Grass_Mesquite" group
tmp <- clone(rel_meco)
tmp$sample_table %<>% subset(Vegetation == "Grass-Mesquite")
tmp$tidy_dataset()
tmp <- trans_network$new(dataset = tmp, cor_method = "spearman", filter_thres = 0.0007)
tmp$cal_network(network_method = "SpiecEasi")
soil_amp_network$GrassMesquite <- tmp


#The function cal_module in meconetcomp package is designed to
#partition modules for all the networks in the list.
soil_amp_network %<>% cal_module(undirected_method = "cluster_fast_greedy")

#we extracted all the res_network_attr tables in the networks and merged them into one final table by using #cal_network_attr function in meconetcomp package.
tmp <- cal_network_attr(soil_amp_network)
  # tmp is a data.frame object

#The get_node_table and get_edge_table functions of meconetcomp package can be used to directly extract node and edge properties for all the networks. The return table is stored in each network object.
soil_amp_network %<>% get_node_table(node_roles = TRUE) %>% get_edge_table

#The nodes in all the networks can be converted to a new microtable object by using the node_comp function of #meconetcomp package. Then, it is easy to analyse the nodes overlap with trans_venn class.

  # obtain the node distributions by searching the res_node_table in the object
tmp <- node_comp(soil_amp_network, property = "name")
  # obtain nodes intersection
tmp1 <- trans_venn$new(tmp, ratio = "numratio")
g1 <- tmp1$plot_venn(fill_color = FALSE, color = c("#679436", "#c1292e", "#e1bc29"))
g1
#ggsave("soil_amp_node_overlap_fungi.png", g1, width = 7, height = 6)
  # calculate jaccard distance to reflect the overall differences of networks
tmp$cal_betadiv()
tmp$beta_diversity$jaccard
tmp$beta_diversity$bray

  
#The pipeline of studying edges overlap is similar with the above operations of nodes comparison. The edge_comp #function of meconetcomp package is used to convert edges distribution to a new microtable object.
  # get the edge distributions across networks
tmp <- edge_comp(soil_amp_network)
  # obtain edges intersection
tmp1 <- trans_venn$new(tmp, ratio = "numratio")
g1 <- tmp1$plot_venn(fill_color = FALSE, color = c("#679436", "#c1292e", "#e1bc29"))
g1
#ggsave("soil_amp_edge_overlap_fungi.png", g1, width = 7, height = 6)

tmp$cal_betadiv()
tmp$beta_diversity$jaccard
tmp$beta_diversity$bray

#Then we extracted the subset of edges according to the intersections of edges across networks, which can be accomplished with the subset_network function in meconetcomp package.
  # first obtain edges distribution and intersection
tmp <- edge_comp(soil_amp_network)
tmp1 <- trans_venn$new(tmp)
  # convert intersection result to a microtable object
tmp2 <- tmp1$trans_comm()
  # extract the intersection of all the three networks ("IW", "TW" and "CW")
  # please use colnames(tmp2$otu_table) to find the required name
#Intersec_all <- subset_network(soil_amp_network, venn = tmp2, name = "Grass&Mesquite&GrassMesquite")
  # Intersec_all is a trans_network object

#To know which taxa constitute the nodes in edges is important in understanding species co-occurrence patterns and answering ecological questions. In this part, as an instance, we used edge_tax_comp function of meconetcomp package to get the sums of node sources (at Phylum level) in the positive edges. In other words, how many linked nodes of positive edges come from different phyla or the same phyla. Then, to make the results comparable, the ratio was calculated with the positive edge number as denominator.

soil_amp_network_edgetax <- edge_tax_comp(soil_amp_network, taxrank = "Phylum", label = "+", rel = TRUE)
# filter the features with small number
soil_amp_network_edgetax <- soil_amp_network_edgetax[apply(soil_amp_network_edgetax, 1, mean) > 0.01, ]
# visualization
g1 <- pheatmap::pheatmap(soil_amp_network_edgetax, display_numbers = TRUE)
g1
#ggsave("soil_amp_edge_tax_comp_fungi.png", g1, width = 7, height = 7)




### trying to plot ###

soil_amp_network$Grass$save_network(filepath = "fungi_grass_network.gexf")
soil_amp_network$Mesquite$save_network(filepath = "fungi_mesquite_network.gexf")
soil_amp_network$GrassMesquite$save_network(filepath = "fungi_grassmesquite_network.gexf")

# calculate network attributes
soil_amp_network$Grass$cal_network_attr()
soil_amp_network$Grass$res_network_attr


soil_amp_network$GrassMesquite$cal_network_attr()
soil_amp_network$GrassMesquite$res_network_attr


soil_amp_network$Mesquite$cal_network_attr()
soil_amp_network$Mesquite$res_network_attr

```


```{r}
# library(SpiecEasi)
# library(file2meco)
# library(mia)
# library(dplyr)
# library(microeco)
# library(magrittr)
# 
# #subset to grass
# grass_ps <- subset_samples(phylo_rm_cntrl, vegetation=="Grass")
# #subset to grass_mesquite
# grass_mesquite_ps <- subset_samples(phylo_rm_cntrl, vegetation=="Mesquite_grass")
# #subset to mesquite
# mesquite_ps <- subset_samples(phylo_rm_cntrl, vegetation=="Mesquite")
# 
# ######## Grass #########
# phylo_grass <- file2meco::phyloseq2meco(grass_ps)
# 
# t1 <- trans_network$new(dataset = phylo_grass, cor_method = NULL, taxa_level = "OTU", filter_thres = 0.001)
# 
# t1$cal_network(network_method = "SpiecEasi", SpiecEasi_method = "mb")
# 
# t1$cal_module(method = "cluster_fast_greedy")
# 
# #t1$save_network(filepath = "network_grass.gexf")
# 
# # calculate network attributes
# t1$cal_network_attr()
# t1$res_network_attr
# 
# 
# # get node properties
# t1$get_node_table(node_roles = TRUE)
# t1$res_node_table
# 
# 
# # get edge properties
# t1$get_edge_table()
# t1$res_edge_table 
# 
# t1$get_adjacency_matrix()
# t1$res_adjacency_matrix
# 
# t1$plot_taxa_roles(use_type = 1)
# 
# 
# # plot node roles with phylum information
# t1$plot_taxa_roles(use_type = 2)
# 
# t1$cal_eigen()
# 
# 
# library(chorddiag)
# 
# t1$cal_sum_links(taxa_level = "Order")
# t1_plot <- t1$plot_sum_links(plot_pos = TRUE, plot_num = 10, color_values = RColorBrewer::brewer.pal(10, "Paired"))
# 
# 
# 
# ######## Grass-mesquite #########
# phylo_grass_mesquite <- file2meco::phyloseq2meco(grass_mesquite_ps)
# 
# t2 <- trans_network$new(dataset = phylo_grass_mesquite, cor_method = NULL, taxa_level = "OTU", filter_thres = 0.001)
# 
# t2$cal_network(network_method = "SpiecEasi", SpiecEasi_method = "mb")
# 
# t2$cal_module(method = "cluster_fast_greedy")
# 
# #t2$save_network(filepath = "network_mg.gexf")
# 
# # calculate network attributes
# t2$cal_network_attr()
# t2$res_network_attr
# 
# 
# # get node properties
# t2$get_node_table(node_roles = TRUE)
# t2$res_node_table
# 
# 
# # get edge properties
# t2$get_edge_table()
# t2$res_edge_table 
# 
# t2$get_adjacency_matrix()
# t2$res_adjacency_matrix
# 
# t2$plot_taxa_roles(use_type = 1)
# 
# 
# # plot node roles with phylum information
# t2$plot_taxa_roles(use_type = 2)
# 
# t2$cal_eigen()
# 
# 
# library(chorddiag)
# 
# t2$cal_sum_links(taxa_level = "Order")
# t2_plot <-t2$plot_sum_links(plot_pos = TRUE, plot_num = 10, color_values = RColorBrewer::brewer.pal(10, "Paired"))
# 
# 
# 
# 
# ######## mesquite #########
# phylo_mesquite <- file2meco::phyloseq2meco(mesquite_ps)
# 
# t3 <- trans_network$new(dataset = phylo_mesquite, cor_method = NULL, taxa_level = "OTU", filter_thres = 0.001)
# 
# t3$cal_network(network_method = "SpiecEasi", SpiecEasi_method = "mb")
# 
# t3$cal_module(method = "cluster_fast_greedy")
# 
# #t3$save_network(filepath = "network_mesquite.gexf")
# 
# # calculate network attributes
# t3$cal_network_attr()
# t3$res_network_attr
# 
# # get node properties
# t3$get_node_table(node_roles = TRUE)
# t3$res_node_table
# 
# # get edge properties
# t3$get_edge_table()
# t3$res_edge_table 
# 
# t3$get_adjacency_matrix()
# t3$res_adjacency_matrix
# 
# t3$plot_taxa_roles(use_type = 1)
# 
# 
# # plot node roles with phylum information
# t3$plot_taxa_roles(use_type = 2)
# 
# t3$cal_eigen()
# 
# 
# library(chorddiag)
# 
# t3$cal_sum_links(taxa_level = "Order")
# t3_plot <- t3$plot_sum_links(plot_pos = TRUE, plot_num = 10, color_values = RColorBrewer::brewer.pal(10, "Paired"))
# 
# 
# t1_plot
# t2_plot
# t3_plot
```


# https://github.com/stefpeschel/NetCoMi
```{r}

# library(NetCoMi)
# 
# 
# grass <- phyloseq::subset_samples(phylo_rm_cntrl, Vegetation == "Grass")
# mesquite  <- phyloseq::subset_samples(phylo_rm_cntrl, Vegetation == "Mesquite")
# grass_mesquite <- phyloseq::subset_samples(phylo_rm_cntrl, Vegetation == "Grass-Mesquite")
# 
# 
# ### Grass to Mesquite ###
# g_m <- netConstruct(grass, mesquite,
#                            filtTax = "highestFreq",
#                            filtTaxPar = list(highestFreq = 750),
#                            zeroMethod = "pseudo",
#                            normMethod = "clr",
#                            measure = "pearson",
#                            verbose = 2)
# 
# g_m1 <- netAnalyze(g_m, clustMethod = "cluster_fast_greedy")
# 
# nclust_g_m <- as.numeric(max(names(table(g_m1$clustering$clust1))))
# 
# col <- c(topo.colors(nclust_g_m ), rainbow(37))
# 
# diff_season_g_m <- diffnet(g_m ,
#                        diffMethod = "fisherTest",
#                        adjust = "bonferroni")
# 
# # Identify the differentially associated OTUs
# diffmat_sums_g_m <- rowSums(diff_season_g_m $diffAdjustMat)
# diff_asso_names_g_m <- names(diffmat_sums_g_m[diffmat_sums_g_m > 0])
# 
# 
# plot(g_m1, 
#       nodeFilter = "names",
#      nodeFilterPar = diff_asso_names_g_m,
#      sameLayout = TRUE, 
#      layoutGroup = "union", 
#      colorVec = col,
#      borderCol = "gray40", 
#      nodeSize = "degree", 
#      cexNodes = 0.9, 
#      nodeSizeSpread = 3, 
#      edgeTranspLow = 0, 
#      edgeTranspHigh = 5,
#      groupNames = c("Grass", "Mesquite"), 
#      showTitle = TRUE, 
#      layout = "circle",
#      cexTitle = 1.8,
#      mar = c(1,1,3,1), 
#      repulsion = 0.9, 
#      labels = TRUE, 
#      rmSingles = "inboth",
#      nodeTransp = 50, 
#      hubTransp = 30)
# 
# 
# # Differential network plot
# 
# plot(diff_season_g_m, 
#      cexNodes = 0.8, 
#      cexLegend = 0.8,
#      layout = "circle",
#      edgeCol = c("#8fe388", "#d00000",  "#ffba08"  , "#ff7b9c", "#3185fc",  "#a68fdd",  "#1b998b",  "#ff9b85",  "grey"),
#      cexLabels = 1.5,
#      legend = FALSE,
#      cexTitle = 1,
#      title = "Differential Network: Grass versus Mesquite",
#      mar = c(4,2,3,2)); legend("bottom", legend = c("G + / M +",
#                             "G + / M -",
#                             "G - / M +"), 
#             col = c("#8fe388", "#ffba08", "#ff7b9c"), xpd=TRUE, inset = 0.02, lty = 1, lwd = 4, cex =
#               0.7, horiz = TRUE)
# 
# 
# 
# ### Grass to Grass-Mesquite ###
# g_gm <- netConstruct(grass, grass_mesquite,
#                            filtTax = "highestFreq",
#                            filtTaxPar = list(highestFreq = 750),
#                            zeroMethod = "pseudo",
#                            normMethod = "clr",
#                            measure = "pearson",
#                            verbose = 2)
# 
# g_gm1 <- netAnalyze(g_gm , clustMethod = "cluster_fast_greedy")
# 
# nclust_g_gm1 <- as.numeric(max(names(table(g_gm1$clustering$clust1))))
# 
# col <- c(topo.colors(nclust_g_gm1), rainbow(37))
# 
# diff_season_g_gm <- diffnet(g_gm,
#                        diffMethod = "fisherTest",
#                        adjust = "bonferroni")
# 
# # Identify the differentially associated OTUs
# diffmat_sums_g_gm <- rowSums(diff_season_g_gm$diffAdjustMat)
# diff_asso_names_diffmat_sums_g_gm <- names(diffmat_sums_g_gm[diffmat_sums_g_gm > 0])
# 
# 
# plot(g_gm1, 
#       nodeFilter = "names",
#      nodeFilterPar = diff_asso_names_diffmat_sums_g_gm,
#      sameLayout = TRUE, 
#      layoutGroup = "union", 
#      colorVec = col,
#      borderCol = "gray40", 
#      layout = "circle",
#      nodeSize = "degree", 
#      cexNodes = 0.9, 
#      nodeSizeSpread = 3, 
#      edgeTranspLow = 0, 
#      edgeTranspHigh = 5,
#      groupNames = c("Grass", "Grass-Mesquite"), 
#      showTitle = TRUE, 
#      cexTitle = 1.8,
#      mar = c(1,1,3,1), 
#      repulsion = 0.9, 
#      labels = TRUE, 
#      rmSingles = "inboth",
#      nodeTransp = 50, 
#      hubTransp = 30)
# 
# 
# # Differential network plot
# plot(diff_season_g_gm, 
#      cexNodes = 0.8, 
#      cexLegend = 0.8,
#      layout = "circle",
#      edgeCol = c("#8fe388", "#d00000",  "#ffba08"  , "#ff7b9c", "#3185fc",  "#a68fdd",  "#1b998b",  "#ff9b85",  "grey"),
#      cexLabels = 1.5,
#      legend = FALSE,
#      cexTitle = 1,
#      title = "Differential Network: Grass versus Grass-Mesquite",
#      mar = c(4,2,3,2)) ; legend("bottom", legend = c("G + / MG +",
#                             "G + / MG -",
#                             "G - / MG +"), 
#                             col = c("#8fe388", "#ffba08", "#ff7b9c"), xpd=TRUE, inset = 0.02, lty =
#                               1, lwd = 4, cex = 0.7, horiz = TRUE)
# 
# 
# ### Mesquite to Grass-Mesquite ###
# m_mg <- netConstruct(mesquite, grass_mesquite,
#                            filtTax = "highestFreq",
#                            filtTaxPar = list(highestFreq = 750),
#                            zeroMethod = "pseudo",
#                            normMethod = "clr",
#                            measure = "pearson",
#                            verbose = 2)
# 
# m_mg1 <- netAnalyze(m_mg, clustMethod = "cluster_fast_greedy")
# 
# nclust_m_mg1 <- as.numeric(max(names(table(m_mg1$clustering$clust1))))
# 
# col <- c(topo.colors(nclust_m_mg1), rainbow(37))
# 
# diff_season_m_mg <- diffnet(m_mg,
#                        diffMethod = "fisherTest",
#                        adjust = "bonferroni")
# 
# # Identify the differentially associated OTUs
# diffmat_sums_m_mg <- rowSums(diff_season_m_mg$diffAdjustMat)
# diff_asso_names_m_mg <- names(diffmat_sums_m_mg[diffmat_sums_m_mg > 0])
# 
# 
# plot(m_mg1, 
#       nodeFilter = "names",
#      nodeFilterPar = diff_asso_names_m_mg ,
#      sameLayout = TRUE, 
#      layoutGroup = "union", 
#      layout = "circle",
#      colorVec = col,
#      borderCol = "gray40", 
#      nodeSize = "degree", 
#      cexNodes = 0.9, 
#      nodeSizeSpread = 3, 
#      edgeTranspLow = 0, 
#      edgeTranspHigh = 5,
#      groupNames = c("Mesquite", "Grass-Mesquite"), 
#      showTitle = TRUE, 
#      cexTitle = 1.8,
#      mar = c(1,1,3,1), 
#      repulsion = 0.9, 
#      labels = TRUE, 
#      rmSingles = "inboth",
#      nodeTransp = 50, 
#      hubTransp = 30)
# 
# 
# # Differential network plot
# 
# 
# plot(diff_season_m_mg, 
#      cexNodes = 0.8, 
#      cexLegend = 0.8,
#      layout = "circle",
#      edgeCol = c("#8fe388", "#d00000",  "#ffba08"  , "#ff7b9c", "#3185fc",  "#a68fdd",  "#1b998b",  "#ff9b85",  "grey"),
#      cexLabels = 1.5,
#      legend = FALSE,
#      cexTitle = 1,
#      title = "Differential Network: Mesquite versus Grass-Mesquite",
#      mar = c(4,2,3,2));legend("bottom", legend = c("M + / MG +",
#                             "M + / MG -",
#                             "M - / MG +"), 
#                             col = c("#8fe388", "#ffba08", "#ff7b9c"), xpd=TRUE, inset = 0.02, lty =
#                               1, lwd = 4, cex = 0.7, horiz = TRUE)
```

```{r}

# par(mfrow = c(1, 3))
# 
# 
# plot(diff_season_g_m, 
#      cexNodes = 0.8, 
#      cexLegend = 0.8,
#      layout = "circle",
#      edgeCol = c("#8fe388", "#d00000",  "#ffba08"  , "#ff7b9c", "#3185fc",  "#a68fdd",  "#1b998b",  "#ff9b85",  "grey"),
#      cexLabels = 1.5,
#      legend = FALSE,
#      cexTitle = 1,
#      title = "Differential Network: Grass versus Mesquite",
#      mar = c(4,2,3,2)); legend("bottom", legend = c("G + / M +",
#                             "G + / M -",
#                             "G - / M +"), 
#             col = c("#8fe388", "#ffba08", "#ff7b9c"), xpd=TRUE, inset = 0.02, lty = 1, lwd = 4, cex =
#               0.7, horiz = TRUE)
# 
# 
# plot(diff_season_g_gm, 
#      cexNodes = 0.8, 
#      cexLegend = 0.8,
#      layout = "circle",
#      edgeCol = c("#8fe388", "#d00000",  "#ffba08"  , "#ff7b9c", "#3185fc",  "#a68fdd",  "#1b998b",  "#ff9b85",  "grey"),
#      cexLabels = 1.5,
#      legend = FALSE,
#      cexTitle = 1,
#      title = "Differential Network: Grass versus Grass-Mesquite",
#      mar = c(4,2,3,2)) ; legend("bottom", legend = c("G + / MG +",
#                             "G + / MG -",
#                             "G - / MG +"), 
#                             col = c("#8fe388", "#ffba08", "#ff7b9c"), xpd=TRUE, inset = 0.02, lty =
#                               1, lwd = 4, cex = 0.7, horiz = TRUE)
# 
# plot(diff_season_m_mg, 
#      cexNodes = 0.8, 
#      cexLegend = 0.8,
#      layout = "circle",
#      edgeCol = c("#8fe388", "#d00000",  "#ffba08"  , "#ff7b9c", "#3185fc",  "#a68fdd",  "#1b998b",  "#ff9b85",  "grey"),
#      cexLabels = 1.5,
#      legend = FALSE,
#      cexTitle = 1,
#      title = "Differential Network: Mesquite versus Grass-Mesquite",
#      mar = c(4,2,3,2));legend("bottom", legend = c("M + / MG +",
#                             "M + / MG -",
#                             "M - / MG +"), 
#                             col = c("#8fe388", "#ffba08", "#ff7b9c"), xpd=TRUE, inset = 0.02, lty =
#                               1, lwd = 4, cex = 0.7, horiz = TRUE)

```
