---
title: '<span style = ''font-size:14pt;''>**Microbial Communities in the changing vegetation of the Chihuahuan Desert 
**</span>'
subtitle: '<span style = ''font-size:12pt;''> Fungi Alpha and Beta Diversity
</span>'
author: "Emily Embury"
date: "`r Sys.Date()`"
output: html_document
---
<style type="text/css">
/* Whole document: */ 
body{
  font-size: 12pt;
}
/* Headers */
h1{
  font-size: 12pt;
}
</style>

---

```{r include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,              
  warning = FALSE,       
  message = FALSE,  
  cache = FALSE,        
  fig.align = "center", 
  fig.height = 4,
  fig.width = 6,
  class.source="bg-warning",
  class.output="bg-success"
)

```


# **Import qiime formatted data**
  - https://blog.codyglickman.com/2018/10/qiime2-to-phyloseq.html

```{r import_data}

library(phyloseq)
library(dplyr)
library(tidyverse)
library(vegan)


load("~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/fungi_dada2_data.RData") 
#contains taxa and otu table


#import metadata
sam <- read.csv("~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/Fungi/fungi_oct_28_metadata.csv", header = TRUE) 
rownames(sam) <- sam$sample.id

#add month_veg row to data
sam$month_veg = paste(sam$month, sam$vegetation, sep="-")

#adjust sample data labels
sam$Vegetation <- factor(sam$vegetation, levels = c("Grass", "Mesquite_grass", "Mesquite"), 
                  labels = c("Grass", "Grass-Mesquite", "Mesquite")) 

sam$Month <- factor(sam$month, levels = c("Oct", "Jan", "Mar", "May", "Jul"), 
                  labels = c("October", "January", "March", "May", "July"))

#compile data into phyloseq object
phylo_raw <- phyloseq(otu_table(seqtab.nochim, taxa_are_rows = FALSE), 
               sample_data(sam), 
               tax_table(taxa))


dna <- Biostrings::DNAStringSet(taxa_names(phylo_raw))
names(dna) <- taxa_names(phylo_raw)
phylo_raw <- merge_phyloseq(phylo_raw, dna)
taxa_names(phylo_raw) <- paste0("ASV", seq(ntaxa(phylo_raw)))
phylo_raw

#Add names to biom table and check phyloseq objects
colnames(tax_table(phylo_raw))= c("Kingdom","Phylum","Class","Order","Family","Genus", "Species")
```

# **remove controls + contaminants**

```{r decontam}
library(decontam)

# threshold 0.5, identifies 0 contaminants
contamdf.prev05 <- isContaminant(phylo_raw, method="prevalence", neg="neg", threshold=0.5)
table(contamdf.prev05$contaminant)


#remove any left over controls so they don't impact rarefy
#remove sample 129 and 93 as it had very low reads after filtering, don't want them to impact rarefy
phylo_rm_cntrl = subset_samples(phylo_raw, sample.id != "Control1" & sample.id != "ControlL2")


```


# **Alpha Diversity**
  - https://joey711.github.io/phyloseq/plot_richness-examples.html
  - https://rpubs.com/lconteville/713954 


- https://doi.org/10.1016/j.resmic.2018.03.004 states that shannon is the best index to use

- "Simpson’s index (D) Estimator of species richness and species evenness: more weight on species evenness" -- https://doi.org/10.4014/jmb.1709.09027 

```{r rarefy}

# Extract abundance matrix from the phyloseq object
OTU1 = as(otu_table(phylo_rm_cntrl), "matrix")
# Coerce to data.frame
OTUdf = as.data.frame(OTU1)

#### rarefy with vegan ####

#view rarefication plot to determine depth to rarefy at
#rarecurve(OTUdf, step = 100, cex = 0.75, las = 1) 

depths <- as.data.frame(sample_sums(phylo_rm_cntrl))
# lowest depth is 17574

rare <- rrarefy(OTUdf, 17574)

#rebuild phyloseq with new rare otu table
rare_phylo <- phyloseq(otu_table(rare, taxa_are_rows = FALSE), 
               sample_data(sam)) 
     
```

```{r alpha_Shannon}

richness <- estimate_richness(rare_phylo)

#Shannon
anova.sh.veg = aov(richness$Shannon ~ sample_data(rare_phylo)$Vegetation*sample_data(rare_phylo)$Month + sample_data(rare_phylo)$proximity1)
summary(anova.sh.veg)

sh.veg <- capture.output(summary(anova.sh.veg))
#write.table(sh.veg, file = "~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/fun_shannon_aov.txt", sep = ",", quote = FALSE, row.names = T)

#post hoc
tukey.sh <- TukeyHSD(anova.sh.veg)
tukey.sh$`sample_data(rare_phylo)$Vegetation`

#Simpson
anova.sim.veg = aov(richness$Simpson ~ sample_data(rare_phylo)$Vegetation*sample_data(rare_phylo)$Month + sample_data(rare_phylo)$proximity1)
summary(anova.sim.veg)

#post hoc
tukey.sim <- TukeyHSD(anova.sim.veg)
tukey.sim$`sample_data(rare_phylo)$Vegetation`

sim.veg <- capture.output(summary(anova.sim.veg))
#write.table(sim.veg, file = "~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/fun_simpson_aov.txt", sep = ",", quote = FALSE, row.names = T)

#check anova assumptions
par(mfrow = c(1,2)) #puts the plots next to each other
qqnorm(anova.sh.veg$residuals) #normal q-q plot, tests normality
qqline(anova.sh.veg$residuals, col = "red") #line of fit on q-q plot
plot(anova.sh.veg$fitted.values, anova.sh.veg$residuals, main = "Residuals vs Fitted", xlab = "Fitted Values", 
     ylab = "Residuals") #residuals vs. fitted, test variance
abline(h=0, col = "red") 



alpha_veg_sh <- plot_richness(rare_phylo, x = "Vegetation", measures = c("Shannon"))
alpha_veg_sh + geom_boxplot()

alpha_mo_sh <- plot_richness(rare_phylo, x = "Vegetation", measures = c("Shannon", "Simpson"))
fun_alpha <- alpha_mo_sh + 
  geom_boxplot(show.legend = FALSE, aes(fill=Vegetation)) +
  theme_linedraw()+
  stat_summary(fun=mean, geom="point", shape=18, size = 2, color="darkgray") +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.1))+ 
  ggtitle ("Fungal Alpha Diversity")+  #change title
 scale_fill_manual(values=c("Mesquite" ="#c1292e", "Grass-Mesquite" = "#e1bc29", "Grass" = "#679436", name = "Vegetation"))

fun_alpha

ggsave(file="~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/images/fun_alpha.png", device = png, plot=fun_alpha, width=7, height=5)
```




# **Beta Diversity**

- http://evomics.org/wp-content/uploads/2016/01/phyloseq-Lab-01-Answers.html
- https://www.youtube.com/watch?v=oLf0EpMJ4yA 

- adonis = essentially an ANOVA for distances
- betadisper = testing for significant different variation


- "Furthermore, beta-diversity measures might be chosen to make it easier to assess a specific hypothesis, such as changes in microbiome composition over time. For example, a Bray Curtis distance that uses all the abundance differences may be more sensitive to examine gradients of diversity with location or time" -- https://doi.org/10.1016/j.csbj.2022.04.032 

-  https://doi.org/10.1111/2041-210X.13115 = proportions and rarefy are the best way to normalize for BC distance in community analyses

  
```{r bray_dist_and_plot}

# calculate Bray-Curtis distance
DistBC <- phyloseq::distance(rare_phylo, method = "bray")

#ordinate bray distances
ordBC <- ordinate(rare_phylo, method = "NMDS", distance = DistBC)


#plot distances
p <- plot_ordination(rare_phylo, ordBC, color = "Vegetation") + 
  geom_point(size = 3, aes(shape = Month)) +
  ggtitle("Fungal Community Composition Across Vegetation Types")+
    theme_linedraw()+
  stat_ellipse()+
  scale_color_manual(values=c("Mesquite" ="#c1292e", "Grass-Mesquite" = "#e1bc29", "Grass" = "#679436", name = "Vegetation"))+
  scale_shape_discrete(name="Month")+
  theme(plot.title = element_text(face = "bold", hjust = 0.5))

p

#library(svglite)
#ggsave(file="~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/images/fun_beta.png", plot=p, width=7, height=5)

```

```{r beta_statistics}
#### Statistics ####

#create data frame of metadata
sampleDF <-  data.frame(sample_data(rare_phylo))

# adonis : Analysis of variance using distance matrices
adonis <- adonis2(DistBC ~ sampleDF$Vegetation*sampleDF$Month, strata = sampleDF$proximity, data = sampleDF)
adonis
adonis_fun <- capture.output(adonis)

#write.table(adonis_fun, file = "~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/fun_beta_adonis.txt", sep = ",", quote = FALSE, row.names = T)

#### significance of vegetation ####
library(pairwiseAdonis)
pairwise.adonis(DistBC, phyloseq::sample_data(rare_phylo)$Vegetation)

#set proximity to vegetation as a random variable
Vegetation = sample_data(rare_phylo)$Vegetation
proximity1 = sample_data(rare_phylo)$proximity1

pairwise.adonis2(DistBC ~ Vegetation, strata = "proximity1", data= data.frame(sample_data(rare_phylo)))

# betadisper - analysis of multivariate homogeneity of group dispersion (variances)
beta <- betadisper(DistBC, sampleDF$vegetation)
anova(beta)
permutest(beta)


#### significance of month ####
library(pairwiseAdonis)
pairwise.adonis(DistBC, phyloseq::sample_data(rare_phylo)$Month)

Month = sample_data(rare_phylo)$Month
proximity1 = sample_data(rare_phylo)$proximity1

pairwise.adonis2(DistBC ~ Month, strata = "proximity1", data= data.frame(sample_data(rare_phylo)))



# betadisper - analysis of multivariate homogeneity of group dispersion (variances)
beta <- betadisper(DistBC, sampleDF$Month)
anova(beta)
permutest(beta)

```

```{r session_info}
library(devtools)
session_info()
```