---
title: '<span style = ''font-size:14pt;''>**Microbial Communities in the changing vegetation of the Chihuahuan Desert 
**</span>'
subtitle: '<span style = ''font-size:12pt;''> FunGUILD
</span>'
author: "Emily Embury"
date: "`r Sys.Date()`"
output: html_document
---
<style type="text/css">
/* Whole document: */ 
body{
  font-size: 12pt;
}
/* Headers */
h1{
  font-size: 15pt;
}
</style>

---

```{r include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,              
  warning = FALSE,       
  message = FALSE,  
  cache = FALSE,        
  fig.align = "center", 
  fig.height = 6,
  fig.width = 9,
  class.source="bg-warning",
  class.output="bg-success"
)

```

# **Import formatted data**

```{r import_data}

library(phyloseq)
library(dplyr)
library(tidyverse)
library(vegan)


load("~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/fungi_dada2_data.RData") 
#contains taxa and otu table


#import metadata
sam <- read.csv("~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/Fungi/fungi_oct_28_metadata.csv", header = TRUE) 
rownames(sam) <- sam$sample.id

#add month_veg row to data
sam$month_veg = paste(sam$month, sam$vegetation, sep="-")

#adjust sample data labels
sam$Vegetation <- factor(sam$vegetation, levels = c("Grass", "Mesquite_grass", "Mesquite"), 
                  labels = c("Grass", "Grass-Mesquite", "Mesquite")) 

sam$Month <- factor(sam$month, levels = c("Oct", "Jan", "Mar", "May", "Jul"), 
                  labels = c("October", "January", "March", "May", "July"))

#compile data into phyloseq object
phylo_raw <- phyloseq(otu_table(seqtab.nochim, taxa_are_rows = FALSE), 
               sample_data(sam), 
               tax_table(taxa))


dna <- Biostrings::DNAStringSet(taxa_names(phylo_raw))
names(dna) <- taxa_names(phylo_raw)
phylo_raw <- merge_phyloseq(phylo_raw, dna)
taxa_names(phylo_raw) <- paste0("ASV", seq(ntaxa(phylo_raw)))
phylo_raw

#Add names to biom table and check phyloseq objects
colnames(tax_table(phylo_raw))= c("Kingdom","Phylum","Class","Order","Family","Genus", "Species")

```

# **remove controls + contaminants**

```{r decontam}
library(decontam)

# threshold 0.5, identifies 0 contaminants
contamdf.prev05 <- isContaminant(phylo_raw, method="prevalence", neg="neg", threshold=0.5)
table(contamdf.prev05$contaminant)


#remove any left over controls so they don't impact rarefy
#remove sample 129 and 93 as it had very low reads after filtering, don't want them to impact rarefy
phylo_rm_cntrl = subset_samples(phylo_raw, sample.id != "Control1" & sample.id != "ControlL2")


#read in funguild data
funguild_taxa <- read.csv("~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/Fungi/all_funguild.csv", header = TRUE)


#add replace taxa table with FunGuild taxa list
library(tidyverse)
funguild_taxa <- funguild_taxa %>% remove_rownames %>% column_to_rownames(var="OTU")
guild <- tax_table(as.matrix(funguild_taxa))

tax_table(phylo_rm_cntrl) <- guild

```


```{r}
# #Clear environment
# rm(list = ls(all.names = TRUE))
# 
# #get taxa from phyloseq object
# psTax <- as.data.frame(phylo_rm_cntrl@tax_table)
# 
# #FUNGuild requires one column named "taxonomy" that follows this format. 
# #k__Fungi;p__Basidiomycota;c__Agaricomycetes;o__Corticiales;f__Corticiaceae;g__Laetisaria;s__Laetisaria_fuciformis
# 
# #Do this by pasting the information from the taxonomic ranks into a column separated by ';'
# psTax$taxonomy <- paste(psTax$Kingdom,psTax$Phylum, psTax$Class, psTax$Order, psTax$Family, psTax$Genus, psTax$Species, sep=";")
# 
# #2. Finish formatting the table for input in FUNGuild. 
# 
# #change row labels to first column
# psTax <- tibble::rownames_to_column(psTax, "OTU_ID")
# 
# 
# #Since we don't need this for FUNGuild, remove the Kingdom, Phylum, Class, Order, Family, Genus & Species columns
# psTax_final <- psTax[, -c(2:8)] 
# 
# #3. Write a csv 
# 
# #write.csv(psTax_final, "~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/Fungi/FunGuild.csv", row.names = FALSE)
# 
# #Proceed to running FUNGuild on command line using the 'FunGuild.csv' file as .txt
```

# **FunGUILD**

  - downloaded new guild.py file from https://github.com/UMNFuN/FUNGuild/blob/master/Guilds_v1.1.py
  - place file in the directory with 'FunGuild.csv'
  - in termial, move to directory that contains the two files
  - run this command: python3 Guilds_v1.1.py -otu FunGuild.txt -db fungi -m -u
  - output:
      Found 5923 matching taxonomy records in the database.
      
      Dereplicating and sorting the result...
      
      FunGuild tried to assign function to 5636 OTUs in 'FunGuild.txt'.
      
      FUNGuild made assignments on 3257 OTUs.
      
      Result saved to 'FunGuild.guilds.txt'

# **Plot FunGuild**      
```{r}
plot_bar(phylo_rm_cntrl, x = "Vegetation", fill = "Trophic.Mode")
```