---
title: '<span style = ''font-size:14pt;''>**Microbial Communities in the changing vegetation of the Chihuahuan Desert 
**</span>'
subtitle: '<span style = ''font-size:12pt;''> Site Weather
</span>'
author: "Emily Embury"
date: "`r Sys.Date()`"
output: html_document
---
<style type="text/css">
/* Whole document: */ 
body{
  font-size: 12pt;
}
/* Headers */
h1{
  font-size: 12pt;
}
</style>

---

```{r include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,              
  warning = FALSE,       
  message = FALSE,  
  cache = FALSE,        
  fig.align = "center", 
  fig.height = 10,
  fig.width = 6,
  class.source="bg-warning",
  class.output="bg-success"
)

```

# **Temperature, humidity, and precipitation data** 

From John Anderson:

- Study 611 Plot G3 -> Study 548 CSIS Block-8 
  - Distance from plot to met station:  ~92m NNW
- Study 611 Plot MG3 -> Study 548 CSIS Block-7   
  - Distance from plot to met station:  ~192m SW
- Study 611 Plot M1 -> Study 548 CSIS Block-11    
  - Distance from plot to met station:  ~135m NNW

**Block 8** Grass site

Anderson, J. 2023. Jornada Basin LTER Cross-scale Interactions Study (CSIS) Block 8 meteorological station: Daily summary data: 2013 - ongoing ver 33. Environmental Data Initiative. https://doi.org/10.6073/pasta/bf8b5899b2e6bace4ceefa48fd3c970b (Accessed 2023-09-10).

**Block 7** Mesquite-Grass

Anderson, J. 2023. Jornada Basin LTER Cross-scale Interactions Study (CSIS) Block 7 meteorological station: Daily summary data: 2013 - ongoing ver 35. Environmental Data Initiative. https://doi.org/10.6073/pasta/c6d90223879a86a0825e3aeddb4b1619 (Accessed 2023-09-11).

**Block 11** Mesquite

Anderson, J. 2023. Jornada Basin LTER Cross-scale Interactions Study (CSIS) Block 11 meteorological station: Daily summary data: 2013 - ongoing ver 32. Environmental Data Initiative. https://doi.org/10.6073/pasta/c11ab044ada8ea13b5e6d1d2e20e7494 (Accessed 2023-09-11).

```{r}
library(ggplot2)
library(lubridate)

weather <- read.csv("Raw_data/JRN_temp_humid/all_weather.csv", header = TRUE)
weather$Date <- as.Date(weather$Date)

#test for significant differences in temp across veg type
aov_temp <- aov(weather$Air_TempC_Avg ~ weather$Month*weather$SiteID)
summary(aov_temp)

par(mfrow = c(1,2)) #puts the plots next to each other
qqnorm(aov_temp$residuals) #normal q-q plot, tests normality
qqline(aov_temp$residuals, col = "red") #line of fit on q-q plot
plot(aov_temp$fitted.values, aov_temp$residuals, main = "Residuals vs Fitted", xlab = "Fitted Values", ylab = "Residuals") #residuals vs. fitted, test variance
abline(h=0, col = "red") 

    # no significant variation between site ID in terms of temp


#test for significant differences in humid across veg type

aov_rh <- aov(weather$Relative_Humidity_Avg ~ weather$Month*weather$SiteID)
summary(aov_rh)

par(mfrow = c(1,2)) #puts the plots next to each other
qqnorm(aov_rh$residuals) #normal q-q plot, tests normality
qqline(aov_rh$residuals, col = "red") #line of fit on q-q plot
plot(aov_rh$fitted.values, aov_rh$residuals, main = "Residuals vs Fitted", xlab = "Fitted Values", ylab = "Residuals") #residuals vs. fitted, test variance
abline(h=0, col = "red") 

  # no significant variation between site ID in terms of rel. humidity


#test for significant differences in precip across veg type

library(dplyr)
only_measured_precip <- filter(weather, Ppt_mm_Tot > 0)
  

aov_precip <- aov(log(only_measured_precip$Ppt_mm_Tot) ~ only_measured_precip$Month*only_measured_precip$SiteID)
summary(aov_precip)

par(mfrow = c(1,2)) #puts the plots next to each other
qqnorm(aov_precip$residuals) #normal q-q plot, tests normality
qqline(aov_precip$residuals, col = "red") #line of fit on q-q plot
plot(aov_precip$fitted.values, aov_precip$residuals, main = "Residuals vs Fitted", xlab = "Fitted Values", ylab = "Residuals") #residuals vs. fitted, test variance
abline(h=0, col = "red") 

### now that I know that there is no significant difference in the site types I will average the daily data points

library("dplyr")                             
 
# Specify data frame
SiteID_mean <- weather %>%
    # Specify group indicator, column, function
    group_by(SiteID, Month) %>%
    # Calculate the mean of the "Frequency" column for each group
    summarise_at(vars(Ppt_mm_Tot),
                 list(Mean_Precip = mean)) 


# Specify data frame
SiteID_mean_weather <- weather %>%
    # Specify group indicator, column, function
    group_by(Date) %>%
    # Calculate the mean of the "x" column for each group
    summarise_at(vars("Ppt_mm_Tot", "Relative_Humidity_Avg", "Air_TempC_Avg"), mean, na.rm = T)

#Add month column      
SiteID_mean_weather$Month = SiteID_mean_weather$Date

SiteID_mean_weather$Month <- as.Date(SiteID_mean_weather$Month)

SiteID_mean_weather$Month <- format(SiteID_mean_weather$Month, format = "%B")


#### plot data

### daily total precipitation w/average data
precip <- ggplot(SiteID_mean_weather[which(SiteID_mean_weather$Ppt_mm_Tot >0),], aes(x=Date, y=Ppt_mm_Tot, color = Month))+
  geom_point() +
  scale_x_date(date_labels = "%B", date_breaks = "1 month")+
    theme_linedraw()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), legend.position = "none")+
  #ggtitle("2022-2023 Monthly Precipitation")+
  ylab("Precipitation (mm)")+
  xlab("Month")+
  scale_colour_manual(values=c("October" ="#c1292e", "January" = "#e1bc29", "March" = "#679436", "May" = "#4895ef" , "July" ="#8187dc"))

### daily average humidity w/average data
relhumid <- ggplot(SiteID_mean_weather, aes(x=Date, y=Relative_Humidity_Avg, color = Month))+
  geom_point() +
  scale_x_date(date_labels = "%B", date_breaks = "1 month")+
  #ggtitle("2022-2023 Monthly Relative Humidity")+
  ylab("Average Relative Humidity")+
  theme_linedraw()+
  theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x   = element_blank(), legend.position = "none") + 
  scale_colour_manual(values=c("October" ="#c1292e", "January" = "#e1bc29", "March" = "#679436", "May" = "#4895ef" , "July" ="#8187dc"))


### daily average temperature w/averages
temp <- ggplot(SiteID_mean_weather, aes(x=Date, y=Air_TempC_Avg, color = Month))+
  geom_point() +
  scale_x_date(date_labels = "%B", date_breaks = "1 month")+
  ggtitle("October 2022- July 2023 Monthly Weather")+
  ylab("Average Air Temperature (C)")+
  theme_linedraw()+
  theme(axis.title.x = element_blank(), axis.text.x = element_blank(),legend.position = "none", axis.ticks.x   = element_blank(), plot.title = element_text(face = "bold", hjust = 0.5)) + 
  scale_colour_manual(values=c("October" ="#c1292e", "January" = "#e1bc29", "March" = "#679436", "May" = "#4895ef" , "July" ="#8187dc"))

library(ggpubr)
weather <- ggarrange(temp, relhumid, precip, ncol=1, nrow=3)
weather

library(svglite)
#ggsave(file="~/Desktop/Master_Data/Masters_R/NMSU_Soil_Microbial_Analysis/images/weather.png", device = png, plot=weather, width=7, height=7)

```

#**Calculate monthly averages**
```{r}
library(dplyr)

weather_avg <- SiteID_mean_weather %>%
  group_by(Month) %>%
  summarise_at(vars(Relative_Humidity_Avg, Ppt_mm_Tot, Air_TempC_Avg), list(name = mean))

#write_csv(weather_avg, "Raw_data/JRN_temp_humid/monthly_avg_weather.csv")
```