---
title: '<span style = ''font-size:14pt;''>**Microbial Communities in the changing vegetation of the Chihuahuan Desert 
**</span>'
subtitle: '<span style = ''font-size:12pt;''> Soil pH
</span>'
author: "Emily Embury"
date: "`r Sys.Date()`"
output: html_document
---
<style type="text/css">
/* Whole document: */ 
body{
  font-size: 12pt;
}
/* Headers */
h1{
  font-size: 15pt;
}
</style>

---

```{r include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,              
  warning = FALSE,       
  message = FALSE,  
  cache = FALSE,        
  fig.align = "center", 
  fig.height = 6,
  fig.width = 9,
  class.source="bg-warning",
  class.output="bg-success"
)

```

# **Soil pH**

- There were issues with the pH soil probe so all data using that probe will not be included in any analyses
- All pH measurements are from soil samples sent to RegenAg

# **Import Data**

```{r}

metadata <- read.csv("Bacteria/CORRECTED_metadata.csv", header = TRUE)

library(dtplyr)
library(tidyverse)
#remove controls to remove NAs
metadata <- metadata %>% drop_na()

#re label 
metadata$vegetation <- factor(metadata$vegetation, levels = c("Grass", "Mesquite_grass", "Mesquite"), 
                  labels = c("Grass", "Grass-Mesquite", "Mesquite"))

metadata$month <- factor(metadata$month, levels = c("Oct", "Jan", "Mar", "May", "Jul"), 
                  labels = c("October", "January", "March", "May", "July"))

```

```{r}
#plot data
library(ggplot2)

pH_plot <- ggplot(metadata, aes(x=month, #change order of x-axis
                          y=soil_pH))+
  geom_boxplot()+
  facet_wrap(~factor(vegetation, levels = c("Grass", "Mesquite_grass", "Mesquite")))+
  stat_summary(fun.y=mean, geom="point", shape=23, color="red", fill="yellow") +
  xlab("Vegetation") + # change x axis label
  ylab("pH") # change y axis label



pH_plot_veg <- ggplot(metadata, aes(x=vegetation, 
                          y=soil_pH))+
  geom_boxplot(show.legend = FALSE, aes(fill = vegetation))+
  theme_linedraw()+
  theme(plot.title = element_text(face = "bold", hjust = 0.5))+
  stat_summary(fun.y=mean, geom="point", shape=23, color="red", fill="yellow") +
  xlab("Vegetation") + # change x axis label
  ylab("pH")+ # change y axis label
  scale_fill_manual(values=c("Mesquite" ="#c1292e", "Grass-Mesquite" = "#e1bc29", "Grass" = "#679436"))+
  ggtitle("Soil pH: Vegatation Variation")

pH_plot_month <- ggplot(metadata, aes(x=month, 
                          y=soil_pH))+
  geom_boxplot(show.legend = FALSE, aes(fill = month))+
  theme_linedraw()+
  theme(plot.title = element_text(face = "bold", hjust = 0.5))+
  stat_summary(fun.y=mean, geom="point", shape=23, color="red", fill="yellow") +
  xlab("Month") + # change x axis label
  ylab("pH") +# change y axis label
  scale_fill_manual(values=c("October" ="#c1292e", "January" = "#e1bc29", "March" = "#679436", "May" = "#4895ef" , "July" ="#8187dc"), name = "month")+
  ggtitle("Soil pH: Seasonal Variation")


```

#**statistical analyses**

  - so overall, there is no significant pairwise change in seasonality in a specific vegetation type. There are monthly differences in pH, but they are not related to vegetation differences.
  
  - as there seems to be a stronger vegetation based driver of pH rather than monthly, I will facet the graph by vegetation
```{r}

#anova of soil pH and vegetation/month
aov_ph <- aov(soil_pH ~ vegetation*month, data = metadata)
summary(aov_ph)

#check anova assumptions
par(mfrow = c(1,2)) #puts the plots next to each other
qqnorm(aov_ph$residuals) #normal q-q plot, tests normality
qqline(aov_ph$residuals, col = "red") #line of fit on q-q plot
plot(aov_ph$fitted.values, aov_ph$residuals, main = "Residuals vs Fitted", xlab = "Fitted Values", 
     ylab = "Residuals") #residuals vs. fitted, test variance
abline(h=0, col = "red") 

#post hoc analysis
ph_tuk <- TukeyHSD(aov_ph)

#view ph:vegetation tukey results
ph_tuk$vegetation

#view ph:month tukey results
ph_tuk$month

```

```{r}

#add P values
library(ggpubr)
library(tidyverse)
library(rstatix)
#### for vegetation plot ####
#tukeyhsd data frame
pH_stat <- aov(soil_pH ~ month*vegetation, data = metadata) %>%
      tukey_hsd() 

#filter to only desired comparisons
ph_stat_veg <- dplyr::filter(pH_stat, grepl("^vegetation", term))

# manually add y position
ph_stat_veg <- ph_stat_veg %>%
 mutate(y.position = c(8.7, 9, 9))

# add p-values to plot
pH_plot_veg + stat_pvalue_manual(ph_stat_veg , label = "p.adj.signif", hide.ns = TRUE)




#### for month plot ####
#tukeyhsd data frame
pH_stat <- aov(soil_pH ~ month*vegetation, data = metadata) %>%
      tukey_hsd() 

#filter to only desired comparisons
ph_stat_month <- dplyr::filter(pH_stat, grepl("^month$", term))

# manually add y position
ph_stat_month <- ph_stat_month %>%
 mutate(y.position = c(1, 1, 1, 1, 1, 1, 9, 1, 8.7, 1))

# add p-values to plot
pH_plot_month + stat_pvalue_manual(ph_stat_month , label = "p.adj.signif", hide.ns = TRUE)

```

```{r session_info}
library(devtools)
session_info()
```